Inferring the Recombinant Genealogy of a Pandemic Pathogen in Real Time

### 2025-08-29 latex/main.tex

%%% TODO: Old version as placeholder. This figure is not yet finalised.
\begin{figure}[h]
    \centering
    \includegraphics[width=0.85\linewidth]{averted_mutations.png}
    \caption{Evidence for recombination events in the ARG. The 356 “robust” recombination events detected by sc2ts are colored according to their classification by rebar (recombinant: purple, non-recombinant: gray). (A) Distribution of time to the MRCA of the sc2ts-identified parents. (B) Distribution of the Pango lineage distance between the sc2ts-identified parents. (C) Distribution of the number of mutations averted by recombination (bottom x-axis), defined as the difference in the number of mutations between a copying path allowing recombination (right y-axis) and an alternative copying path disallowing recombination (top x-axis). (D) Copying patterns of five select recombinants.}
    \label{fig:averted_mutations}
\end{figure}

>>>>

%%% TODO: Old version as placeholder. This figure is not yet finalised.
\begin{figure}[h]
    \centering
    \includegraphics[width=1\linewidth]{fig_recombinant_evidence.pdf}
    \caption{Evidence for recombination in the ARG. All plots show “robust” sc2ts recombination nodes, colored according
to their classification by rebar (recombinant: purple, non-recombinant: gray).
(A) Upper: jittered scatterplot comparing number of mutations when recombination allowed ($y$: right axis)
versus an alternative copying path disallowing recombination ($x$: top axis);
recombination nodes in Table \ref{tab:pango_x_lineages} are labelled, point sizes reflect number of descendants;
Lower: recombination nodes classified by number of mutations averted by allowing recombination (i.e. $x$-$y$).
(B) Distribution of time to the MRCA of the parents of each robust recombination node.
(C) Distribution of the Pango lineage distance between parents.
(D) Copying patterns leading to XA, XBB, XBB.1, and the recombinant origin of XZ+XAC+XAD+XAE+XAP;
each recombination node is a mix of variants matching the left parent (green), the right parent (blue), and de-novo mutations (gold).}
    \label{fig:averted_mutations}
\end{figure}
